Lens Modeling in \sw

### 2013-09-10 text/tex/results.tex
more edits

\section{The lens modeling challenge} \label{sec:results}

\subsection{\sw} \label{sec:SpaceWarps}
some words about \sw

@@

In order to estimate users performance, \sw included some simulated lensing configurations in their image set.

There are three kinds of simulated lenses.

Sims produced using {\tt gravlens}
\citep{2001astro.ph..2341K,2001astro.ph..2340K}.

@@

We made use of the simulated lenses (sims) to test the volunteers abilities to model those sims.

The testing was done with a small number of volunteers ($N_\text{v}=4$) and a set of simulated configurations ($N_\text{sim}=29$) chosen to represent some typical configurations.
The volunteers were given an introduction video explaining the theory behind gravitational lensing and the usage of \spl.
Additionally the volunteers had the opportunity to pose general questions to the experts during several hangouts during the training phase that preceded the modeling challenge.\footnote{No questions about the to be modeled sims were answered.}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/spaghetti.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/ASW0001hpf/arriv.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/ASW0001hpf/extr_points.png}}
  \caption{Examples of Spaghetti input (left top) and modeled arrival time surface (right top) vs reconstructed arrival time surface from simulation parameters (bottom left), additionally using a extremal point detector (bottom right).
  \label{fig:output_compare}}
\end{figure}

>>>>

\section{A lens modeling challenge} \label{sec:results}

% \subsection{\sw} \label{sec:SpaceWarps} some words about \sw

Interested volunteers from the \sw forum were initially introduced to
\spl through a video tutorial and by videocon.  After this
introductory stage, a modelling challenge was presented.  This
consisted of 29 simulated lenses (sims) covering a range of lensing
configurations.

@@

The sims were generated by AM, in consultation with PM and AV.  In the
interest of blind testing, the information in this section was
revealed neither to RK, while choosing the challenge set, nor to the
people making models (EB, CC, CM, JO, PS and JW) until they were done.

The sims produced using {\tt gravlens}
\citep{2001astro.ph..2341K,2001astro.ph..2340K} and were of three
kinds, as follows.

@@

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/spaghetti.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/ASW0001hpf/arriv.png}}
%  \subfigure{\includegraphics[width=0.45\textwidth]
%             {fig/sims/ASW0001hpf/extr_points.png}}
  \caption{Examples of Spaghetti input (left top) and modeled arrival time surface (right top) vs reconstructed arrival time surface from simulation parameters (bottom left), additionally using a extremal point detector (bottom right).
  \label{fig:output_compare}}
\end{figure}
